Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2020-01-28 WRITEUP/ms_referee.tex
re-circulate

The simulation zooms in on a galaxy named after the flower \flower, whose properties are given in \citet{Pallottini17a} and are briefly summarized in the following. \flower is a Lyman-break galaxy that at $z\simeq 6$ is hosted by a dark matter halo of mass 
{\bf $M_{\rm DM}\simeq$\eq3.5\,$\times$\,10$^{11}$\,\Msun} at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. \flower has a stellar mass of {\bf $M_\star\simeq$\,2.6\E{10}\,\Msun}, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne.
%
The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang16a}. The effective stellar radius of \flower is $\simeq$\,0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
{\bf The stellar-to-halo mass ratio of \flower ($M_\star/M_{\rm DM}$\eq0.07) is 
between?? those from abundance matching reported by \citet{Moster13a},
but higher than those reported based on other zoom-in simulations at similar redshifts 
(e.g., \citealt{Ceverino17a, Katz17a}, and \citealt{Behroozi19a}). This can result from different feedback implementations.
}

@@

The {\bf total} pressure\footnote{{\bf Non-thermal pressure dominates the total pressure.}} of MCCs identified at the highest $n_{\rm cut}$ ranges from $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$. Such high pressures are comparable to those observed in local ULIRGs; however, the molecular clouds in those are concentrated within their central regions \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
In local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}. On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{Kohandel19a} and higher velocity accretion/SN-driven outflows \citep{Gallerani18a}. The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2. For instance, \citet{Swinbank11a} report ISM pressure of $P/k_B\sim$10$^7$\,K\,\cc and molecular gas mass of $M_{\rm gas}\simeq10^{8-9}$\,\Msun in the star-forming regions of a gas-rich starburst galaxy at \z\eq2.3 based on spatially resolved CO line \obs.

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_1.2}.pdf}
\caption{
Toomre $Q$ maps derived from the central $R$\eq1.2\,kpc of \flower. Contribution from the gas ($Q_{\rm gas}$) and the stellar ($Q_\star$) components is shown in the left and middle panels, respectively. The effective two-component Toomre $Q_{\rm eff}$ parameter map is shown in the right panel.
%
All maps are projected onto the plane of the disk, and a gaussian smoothing of width 30\,pc has been applied to the maps.
%
Positions of MCCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols. Some MCCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$ are likely gravitationally unstable.
%
Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region} reflects the fact that stellar component plays an important role in governing the stability of MCCs against $m=0$  perturbations in relatively evolved and enriched systems at high redshifts.
\label{fig:Qeff}}
\end{figure*}

>>>>

The simulation zooms in on a galaxy named after the flower \flower, whose properties are given in \citet{Pallottini17a} and are briefly summarized in the following. \flower is a Lyman-break galaxy that at $z\simeq 6$ is hosted by a dark matter halo of mass 
{\bf $M_{\rm DM}\simeq$\eq3.5\,$\times$\,10$^{11}$\,\Msun} at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. \flower has a stellar mass of {\bf $M_\star\simeq$\,2.6\E{10}\,\Msun}, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne.
%
The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang16a}. The effective stellar radius of \flower is $\simeq$\,0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
{\bf The stellar-to-halo mass ratio of \flower is $M_\star/M_{\rm DM}$\eq0.07.
Depending on the work considered, this ratio from abundance matching vary when the halo mass is away from $M_h$\ssim10$^{12}$\,\Msun (see e.g., \citealt{Moster13a, Behroozi13b, Behroozi15a, Moster18a}). The ratio of \flower is higher than e.g., \citet{Katz17a}  and \citet{Ceverino17a} which could be a result of different feedback implementation.
}

@@

The {\bf total} pressure\footnote{{\bf Non-thermal pressure dominates the total pressure.}} of MCCs identified at the highest $n_{\rm cut}$ ranges from $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$. Such high pressures are comparable to those observed in local ULIRGs; however, the molecular clouds in these local galaxies are concentrated within their central regions \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to {\bf the highly turbulent nature} of these molecular structures. 
%
{\bf While MCCs in both local ULIRGs and \flower may form via gravitational instability (see e.g., \citealt{McKee07a}), MCCs in the local merger-driven ULIRGs}
are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}; {\bf see \Sec{Qeff} for Toomre-$Q$ analysis on \flower}). {\bf As shown 
by \citet{Kohandel19a} and \citet{Gallerani18a}, the highly turbulent nature seen in the MCCS of \flower result from} extra-planar flows and higher velocity accretion/SN-driven outflows. The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2. For instance, \citet{Swinbank11a} report ISM pressure of $P/k_B\sim$10$^7$\,K\,\cc and molecular gas mass of $M_{\rm gas}\simeq10^{8-9}$\,\Msun in the star-forming regions of a gas-rich starburst galaxy at \z\eq2.3 based on spatially resolved CO line \obs.

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_1.2}.pdf}
\caption{
Toomre $Q$ maps derived from the {\bf central region} of \flower. Contribution from the gas ($Q_{\rm gas}$) and the stellar ($Q_\star$) components is shown in the left and middle panels, respectively. The effective two-component Toomre $Q_{\rm eff}$ parameter map is shown in the right panel.
%
All maps are projected onto the plane of the disk, and a gaussian smoothing of width 30\,pc has been applied to the maps.
%
Positions of MCCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols. Some MCCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$ are likely gravitationally unstable.
%
Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region} reflects the fact that stellar component plays an important role in governing the stability of MCCs against $m=0$  perturbations in {\bf this} relatively evolved and enriched systems at high redshifts.
\label{fig:Qeff}}
\end{figure*}
